Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-21 paper/ijcai/paper.tex
refs + s4.4

This subsection aims to report the performance of the \ds{} technique on slicing de
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top
$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction 
of 30.23\% on average in the projects considered in our study.

@@

In this section, we answer the research questions proposed and discuss the results obtained.
Our approach was capable of slicing a total of $260$ faults from $5$ different 
projects. The remaining faults were not considered because (1) faults
belong to the \closure{} project which requires high CPU to perform the \combpar{k} evaluation 
or (2) faults whose test outputs were not reproducible in the machine used to run the experiments.
\textbf{RQ1} reviews one of the main issues of \ds{} - missing faulty statements - whereas \textbf{RQ2}
discusses how effective is the proposed approach, \combpar{k}.

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes of the projects. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, an improvement
of $5.2\%$. $33$ of the $260$ faults do not include the faulty statements in the slicer report
after slicing.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \ds{}.

The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the 
faulty statements of the \chart{}
project. Table , reports the average rank of all faulty statements for each version of \chart{} project after
applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.

Table \ref{fig:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.

Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant. Shapiro-Wilk ~\cite{10.2307/2333709} tests the null hypothesis that results are drawn from a normal distribution. The test is perfomed for the three techniques under evaluation (\sfl{}, \comb{}-5, \comb{}-10). With 99 \% of confidence, the results tell us that the distributions are not normal. Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman~\cite{10.2307/2279372}. The null-hypothesis is that all distributions are the same. With 99 \% of confidence, the results show that the distributions are not all the same. In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis. Figure \ref{fig:performance} report the results of that analysis for all the distributions. With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean & \textbf{580.0} (584.3)   &  \textbf{502.6} (516.4)  & \textbf{567.0} (679.7)  & \textbf{491.5} (614.0)   \\ \midrule
Median & \textbf{47.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

\begin{figure}[h]
	\vspace{-1.5cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results}
		\label{fig:performance}
\end{figure}

@@

\Mar{moved from intro$\rightarrow$} It is worth noting that Automated
Program Repair techniques should directly benefit from these
results---either to improve their results or to be aware they should
not invest on this integration.

@@

\section{Conclusions and Future Work}
\label{sec:conc}
%
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (DS)
and Spectrum-based Fault Localization (SFL) are very popular fault diagnosis t
echniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining DS with SFL. The results of our empirical study show that, in
practice, DS rarely misses faulty statements (23 misses in 260 cases) and that
the DS-SFL combination improves the diagnostic accuracy in 51\% of the faults.
Hence, we found that, despite tacit opinions of the research community about
the usefulness of DS in automated debugging, we found the combination practical
and effective, and encourage new SFL techniques to be evaluated against that
optimization.

@@

%
%\section*{Acknowledgments}
%include only after review.

{
  \small
  \balance
  \bibliographystyle{named}
  \bibliography{paper}
}

>>>>

This subsection aims to report the performance of the \ds{} technique on slicing de
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top
$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction 
of 30.23\% in the projects considered in our study.

@@

In this section, we answer the research questions proposed and discuss the results obtained.
Our approach was capable of slicing a total of $260$ faults from $5$ different 
projects. The remaining faults were not considered because (1) faults
belong to the \closure{} project which requires high CPU to perform the \combpar{k} evaluation 
or (2) faults whose test outputs were not reproducible in the machine used to run the experiments.
\textbf{RQ1} reviews one of the main issues of \ds{} - missing faulty statements - whereas \textbf{RQ2}
discusses how effective is the \combpar{k} approach against \sfl{}$^{k}$.

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault, we 
only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, \combpar{10} misses less
$5.2\%$ of the faults against \sfl{}$^{10}$.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \sfl{}.
Table~\ref{table:st}, reports the average rank of all faulty statements of all \dfj{} faults considered
to the study after applying the both techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. $33$ of 
the $260$ faults do not include the faulty statements in the slicer report after slicing. Thus, we report
both values in Table~\ref{table:st}. In bold, we present the results of the $227$ faults that do not
contain the cases where the faulty statements where removed using \combpar{k}. Inside parentheses,
we present the rank results for all faults. The \combpar{k} combination yields an improvement of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$. Instead, if $K=10$ is considered the proposed approach returns an improvement of $11.1$ 
on the rank mean of faulty statements. It is worth noting that Automated Program Repair techniques may directly benefit from this
study to improve their results.
Figure \ref{fig:diagnosis} reports the performance of the diagnosis using \combpar{5} and \combpar{10} against
\sfl{}$^{5}$ and \sfl{}$^{10}$, respectively. Although this dataset has more than 50\% of fault of omissions,
our simple slicing approach was capable of improving the ranking of $97$ for $k=5$ and $117$ for $K=117$ faults. 
Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant. Shapiro-Wilk tests the null hypothesis that results are drawn from a normal distribution. The test is perfomed for all techniques and its variants. With 99\% of confidence, the results tell us that the distributions are not normal. Given that $C$ is not normally distributed, we use the non-parametrical statistical hypothesis test, Friedman. The null-hypothesis is that the ranking results of all techniques and variants are the same. With 99\% of confidence, the results show that the distributions are distinct. In order to understand if there exist a pair of distributions that are equal, we performed a Siegel post-hoc analysis. Figure \ref{fig:performance} reports the results of Siegel analysis for all the distributions. With 99\% of confidence, it is possible to see that in general the distributions are very similar.

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean & \textbf{580.0} (584.3)   &  \textbf{502.6} (516.4)  & \textbf{567.0} (679.7)  & \textbf{491.5} (614.0)   \\ \midrule
Median & \textbf{47.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.43 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.12 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.00 x $10^{-24}$} & \makecell{$W$ = 0.47 \\ $p$ = 1.62 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

\begin{figure}[h]
	\vspace{-1.5cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
\end{figure}

@@

@@

\section{Conclusions and Future Work}
\label{sec:conc}
%

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (DS)
and Spectrum-based Fault Localization (SFL) are very popular fault diagnosis t
echniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining DS with SFL. The results of our empirical study show that, in
practice, DS rarely misses faulty statements (23 misses in 260 cases) and that
the DS-SFL combination improves the diagnostic accuracy in 51\% of the faults.
Hence, we found that, despite tacit opinions of the research community about
the usefulness of DS in automated debugging, we found the combination practical
and effective, and encourage new SFL techniques to be evaluated against that
optimization.

@@

%
%\section*{Acknowledgments}
%include only after review.
{
  \small
  \balance
  \bibliographystyle{named}
  \bibliography{paper}
}
